---
title: "Epi Results using LCM Exposure Models"
author: "Magali Blanco"
date: ' `r Sys.time()` '
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    number_sections: true
    toc_float: true
    collapsed: false
    smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

# Setup 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, 
                      cache=F, cache.comments = F, 
                      message = F, warning = F, 
                      tidy.opts=list(width.cutoff=60), tidy=TRUE#, fig.height = 10, fig.width = 10
                      )  

# Clear workspace of all objects and unload all extra (non-base) packages
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
           detach, character.only=TRUE, unload=TRUE, force=TRUE))}

pacman::p_load(tidyverse, kableExtra)    

dt_path <- file.path("Output", readRDS(file.path("Output", "latest_dt_version.rda")))

set.seed(1)

source("functions.R")
output_data_path <- file.path(dt_path, "epi")

image_path <- file.path("..", "Manuscript", "Images", "v4", "other", "lcm")
if(!dir.exists(image_path)) {dir.create(image_path, recursive = T)}
# ggplot settings
theme_set(theme_bw())
theme_update(legend.position = "bottom")

##################################################################################################
# LOAD DATA
##################################################################################################
# reference models
## stataionary and LCM
st_ref_model <- "full_ST" #ST 
sp_ref_model <- "full_SP" # SP 
## no LCM
st_ref_model2 <- "fptv_no" #ST 
sp_ref_model2 <- "fp_no" # SP 


cw <- read.csv(file.path(dt_path, "model_cw_lcm.csv")) %>%
  mutate(model = gsub("pm25_", "", model))

# person-level exposures 
cs <- readRDS(file.path(output_data_path, "dt_for_cross_sectional_analysis_lcm.rda")) %>%
  rename(exposure = avg_0_5_yr) %>%  
  select(-starts_with("avg_")) %>%
  mutate(model = gsub("pm25_", "", model)) %>%
  left_join(select(cw, model, model_type)) %>%
  #drops 1 person that the "full" model has missing values for
  drop_na(exposure)


# --> START HERE. ERROR. WHY WON'T MODEL FACTOR SO LAST PLOT IS REARRANGED??
# health effect estimates & CW
model_coefs <- readRDS(file.path(output_data_path, "model_coefs_lcm.rda")) %>%
  mutate(variable="PM2.5",
         model = gsub("pm25_", "", model),
         model = as.factor(model),
         #model = relevel(model, ref=st_ref_model),
         ref_model = ifelse(model %in% c(st_ref_model, sp_ref_model), "Full Model", "Alternative LCM Model"),
         ref_model = factor(ref_model, levels=c("Full Model", "Alternative LCM Model"))) %>%
  left_join(cw) #%>% filter(model != sp_ref_model)

#model_coefs$model

```

# Model definitions


```{r}
model_coefs %>%
  select(model, method, model_type, variable) %>% 
  arrange(method) %>%
  kable() %>% 
  kable_styling()

```

# Model R2

JB should have this.

# Participant Exposure Predictions 

comparison of predicted 5 yr exposures at baseline

```{r}
# plot
st_cs <- cs %>%
  filter(model_type=="ST") %>%
  select(-c(exp_coverage, exact_coverage, imp_coverage, imputation_quality)) %>%
  pivot_wider(names_from = model, values_from = exposure) %>%  
  rename(full_model = st_ref_model) %>%  
  pivot_longer(cols = starts_with(c("fptv_")))
  
sp_cs <- cs %>%
  filter(model_type=="SP") %>%
  select(-c(exp_coverage, exact_coverage, imp_coverage, imputation_quality)) %>%
  pivot_wider(names_from = model, values_from = exposure) %>%
  rename(full_model = sp_ref_model) %>%  
  pivot_longer(cols = starts_with(c("fp_", "rp_")))
  
print("the full model is our default epi model with stationary and LCM")
rbind(st_cs, sp_cs) %>%  
  ggplot(aes(x=full_model, y=value, col=name)) +
  facet_wrap(~model_type, scales="free") +
  geom_point(alpha=0.05) +
  geom_smooth() +
  geom_abline(slope = 1, intercept = 0, linetype=2) + 
  labs(col="LCM Model", y="LCM Model Prediction", x= "Full ST PM2.5 Model Prediction")

ggsave(file.path(image_path, "5yr_exposure_comparisons.png"), width = 8, height = 6)

#table
cs %>%
  group_by(model, model_type) %>%
  alt_boxplot(var="exposure") %>%
  rename(Q2.5=Qmin, Q97.5=Qmax) %>%
  kable(caption = "Distribution of PM2.5 ug/m3) predictions", 
        digits = 0, format.args = list(big.mark=",")) %>% 
  kable_styling()

```

**Correlations**: exposure predictions from all models generate highly correlated predictions

# --> is this right? some correlations are 1.0, most are very low 

```{r}
comparison_models <- setdiff(unique(cs$model), st_ref_model) %>% setdiff("full_SP")

cs %>%
  select(study_id, exposure, model) %>%
  filter(model != sp_ref_model) %>%
  pivot_wider(names_from = model, values_from = exposure) %>%  
  pivot_longer(cols = comparison_models) %>%  
  # 1 person doesn't have ST full predictions
  drop_na(st_ref_model) %>%
  group_by(name) %>% 
  summarize(correlation = cor(get(st_ref_model), value)) %>%
  kable(caption = "Correlation (R) of fptv_no predictions with predictions from other methods", 
        digits = 2, 
        col.names = c("Model", "Correlation with fptv_no")) %>%
  kable_styling()

```

# Comparison of health effect estimates (CASI-IRT)

the resulting health estimates from using UK-PLS and various ML UFP exposure models is similar, with random forests & spatcv being the most different (~25-35% lower point estimate)

### --> edit? drop full_SP or give it its own vertical line?

```{r}
ref_beta <- model_coefs$est[model_coefs$model==st_ref_model]

print("adjustd association between P-TRAK UFP (1k pt/cm3) and CASI-IRT")
model_coefs %>%
  ggplot(aes(y=model, col=ref_model)) +  
  facet_grid(vars(model_type), scales = "free_y", switch = "y", space="free") +
  geom_vline(xintercept = ref_beta, linetype=1, alpha=0.5) +
  geom_vline(xintercept = 0, linetype=2, alpha=0.2) +
  geom_pointrange(aes(x=est, xmin=lower, xmax=upper), size=0.5, alpha=0.8, orientation = "y") +
  scale_x_continuous(sec.axis = sec_axis(
    trans=~(.-ref_beta)/-ref_beta, name="% Difference from Full ST Model", labels = scales::percent, breaks = c(-1.5,0, 1.5))) +
  labs(col = NULL,
           y="LCM Model",
           x = "Coefficient Estimate (95% CI)")

ggsave(file.path(image_path, "pm25_health_estimate.png"), width = 6, height = 8)

```



