---
title: "Campaign Predictions Summary"
author: "Magali Blanco"
date: ' `r Sys.time()` '
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    number_sections: true
    toc_float: true
    collapsed: false
    smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

# Setup 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, 
                      cache=F, cache.comments = F, 
                      message = F, warning = F, 
                      tidy.opts=list(width.cutoff=60), tidy=TRUE#, fig.height = 10, fig.width = 10
                      )  

# Clear workspace of all objects and unload all extra (non-base) packages
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
           detach, character.only=TRUE, unload=TRUE, force=TRUE))
}

pacman::p_load(tidyverse, 
               PRISMAstatement,table1,
               knitr, kableExtra
               #ggpmisc #add line fit parameters to ggplot()
               )    

set.seed(1)

source("functions.R")
output_data_path <- file.path("Output", "epi")
image_path <- file.path("..", "Manuscript", "Images")


# ggplot settings
theme_set(theme_bw())
theme_update(legend.position = "bottom")

```

```{r}
##################################################################################################
# LOAD DATA
##################################################################################################
#main_pollutants <- readRDS(file.path(output_data_path, "main_pollutants.rda"))

campaign_descriptions <- readRDS(file.path("Output", "Selected Campaigns", "selected_campaigns_v2.rda")) %>%
  label_pollutants() %>% label_designs() #%>%
  # --> upate this to restrict descriptives to e.g., pollutants  
  #filter(grepl("PNC", variable))

all_pollutants_labels <- unique(campaign_descriptions$variable)
main_pollutants_labels <- all_pollutants_labels[str_detect(all_pollutants_labels, "Total")]


cs <- readRDS(file.path(output_data_path, "dt_for_cross_sectional_analysis.rda")) %>%
  rename(model_id = model,
         exposure = avg_0_5_yr) %>%
  right_join(select(campaign_descriptions, model_id, variable, design, version, campaign), by="model_id") 

model_coefs0 <- readRDS(file.path(output_data_path, "model_coefs.rda"))

model_coefs <- model_coefs0 %>% 
  filter(model_id %in% campaign_descriptions$model_id) %>%
  label_pollutants() %>% label_designs()

exclusion_table <- read.csv(file.path(output_data_path, "exclusion_table.csv"))

#for boxplots
bp_min <- 0.025
bp_max <- 0.975

```

# Study Dates 

```{r}
range(cs$visitdt)

```

# QC variables

these QC variable values from the exposure (issue 17) & health (issue 12) dataset should be identical or very similar, and they are. 

```{r}
# names(cs)
qc_vars <- c("exp_coverage", "avg_wc_no2_MM_05_yr",
           "exact_coverage", "avg_ec_no2_MM_05_yr",
           "imp_coverage", "avg_ic_no2_MM_05_yr", 
           "imputation_quality", "avg_iq_no2_MM_05_yr")

cs %>%
  # person-level dataset
  select(study_id, all_of(qc_vars)) %>%
  distinct() %>%
  pivot_longer(cols = -study_id, names_to = "var", values_to = "value") %>%
  mutate(var=factor(var, levels=qc_vars)) %>%
  group_by(var) %>%
  summarize(
    N = n(),
    Min = min(value),
    Q25 = quantile(value, 0.25),
    Median = median(value),
    Mean = mean(value),
    Q75 = quantile(value, 0.75),
    Max = max(value)
  ) %>%
  kable(caption = "QC variables", digits = 2) %>%
  kable_styling()

```


# Exposure

## Correlations

# --> comprea UFP bins, ?no2

```{r}

```



## R2

30 campaigns per design-version-pollutant 

```{r}
t2 <- campaign_descriptions %>%
  filter(variable %in% main_pollutants_labels) %>%
  group_by(variable, design, version) %>%
  alt_boxplot(var = "MSE_based_R2", min_q=bp_min, max_q=bp_max) %>%
  ungroup()
 
t2 %>%
  kable(caption = "Distribution of MSE-based R2 for each design", 
        digits = 2) %>%
  kable_styling()

print("dashed line is the All Data design performance")

#t2 %>%
campaign_descriptions %>%
  filter(variable %in% main_pollutants_labels,
         design != "All Data") %>%
  ggplot(aes(x=version,
             y=MSE_based_R2
             )) + 
  geom_hline(data=select(filter(t2, design=="All Data"), variable, Q50), aes(yintercept = Q50), linetype=2, alpha=0.5) + 
  geom_boxplot(
   #  aes(ymin = Qmin, lower = Q25, middle = Q50, upper = Q75, ymax = Qmax),
   # stat = "identity"
   ) + 
  facet_grid(variable~design, scales = "free", switch = "both") + 
  labs(y = "MSE-Based R2",
       x = "Design" #x = "Design-Version"
       )

ggsave(file.path(image_path, "SI", "r2.png"), width = 6, height = 6)

```


## prediction comparisons

N_predictions = 65400 participant predictions = 30 campaigns * 2128 participants/campaign

```{r}
t1 <- cs %>%
  filter(variable %in% main_pollutants_labels) %>%
  group_by(variable, design, version) %>%
  alt_boxplot(var = "exposure")  #%>% label_pollutants() %>% label_designs() 

t1 %>%
  kable(caption = "Predicted exposures by design", 
        digits = 1) %>%
  kable_styling()

t1 %>%
  mutate(variable = gsub(" \\(", "\\\n(", unique(variable))) %>%
  ggplot(aes(x=version)) + 
   geom_boxplot(aes(ymin = Qmin, lower = Q25, middle = Q50, upper = Q75, ymax = Qmax),
   stat = "identity") + 
  facet_grid(variable~design, scales = "free", switch = "both") + 
  labs(y = "Predicted Exposure",
       x = "Design" #x = "Design-Version"
       )

ggsave(file.path(image_path, "SI", "predicted_exposure.png"), width = 6, height = 6)

```




## Compare Design Predictions

```{r}
full <- cs %>% 
  filter(grepl("All Data", design),
         variable %in% main_pollutants_labels
         ) %>%
  select(study_id, variable, exposure, model_id) %>%
  rename(full_prediction = exposure)

designs <- filter(cs, 
                  variable %in% main_pollutants_labels,
                  !model_id %in% full$model_id) %>%
  select(study_id, variable, exposure, model_id, design, version, campaign) %>%
  rename(design_prediction = exposure)

comp <- left_join(select(full, -model_id), designs)

```

scatter plots/best fit lines: design prediction vs full prediction

```{r, fig.height=8}
# x = main_pollutants_labels[1]
lapply(main_pollutants_labels, function(x){
  p <- comp %>%
    filter(variable==x) %>%
    ggplot(aes(x=full_prediction, y=design_prediction, col=campaign
               )) + 
    facet_wrap_equal(~design+version) + 
    geom_abline(intercept=0, slope = 1, linetype=2, alpha=0.5, size=0.2) +
    #geom_pointdensity() +
    stat_smooth(geom="line", method="lm", aes(group=campaign), alpha=0.3, size=0.5) +
    stat_smooth(geom="line", method="lm", size=1.2) +
    #stat_poly_line() +
  # stat_poly_eq(aes(label = paste(after_stat(eq.label),
  #                                after_stat(rr.label), sep = "*\", \"*"))) +
     
    labs(x = "All Data Prediction", y = "Design Prediction",
         title = x
         )
  
  print(p)
  
  ggsave(file.path(image_path, "SI", paste0("prediction_comp_", gsub("\\,.*| .*", "", x), ".png")), width = 8, height = 6)

})

```

correlations (N= 30 correlations for each design-version)

```{r}
corr_table <- comp %>%
  group_by(variable, design, version, campaign) %>%
  summarize(n=n(),
            r = cor(full_prediction, design_prediction)) #%>%
  # group_by(variable, design, version) %>%
  # alt_boxplot(var = "r", min_q=bp_min, max_q=bp_max) 

corr_table %>%
  group_by(variable, design, version) %>%
  alt_boxplot(var = "r", min_q=bp_min, max_q=bp_max) %>%
  
  kable(caption = "Distribution of Pearson correlations (R) between full campaign and sampling design predictions (N= 30 correlations for each design-version)", 
        digits = 2) %>%
  kable_styling()

corr_table %>%
    ggplot(aes(x=version, 
               y=r
               )) + 
  geom_boxplot(
    #aes(ymin = Qmin, lower = Q25, middle = Q50, upper = Q75, ymax = Qmax), stat = "identity"
    ) + 
  facet_grid(variable~design, scales = "free", switch="both") + 
  labs(y = "Pearson Correlation (R)",
       x = "Design" #x = "Design-Version"
       )

ggsave(file.path(image_path, "SI", "prediction_correlations.png"), width = 6, height = 6)

```

# CASI

```{r}
# person-level dataset
pop <- cs %>%
  filter(variable %in% main_pollutants_labels,
         design== "All Data") %>% 
  group_by(variable) %>%
  mutate(high_exposure = exposure > median(exposure),
         visit_age = visit_age_centered75+75
         ) %>%
  distinct(study_id, casi_irt, visit_age, year2, apoe, male, degree, 
           #race_white, 
           variable, exposure, high_exposure) %>%
  pivot_wider(names_from = variable, values_from = c(high_exposure, exposure))  

names(pop) <- gsub("\\ .*|\\,.*", "", names(pop))
```

```{r}
pop %>%
  alt_boxplot(var="casi_irt") %>%
  kable(caption = "Distribution of CASI-IRT", 
        digits = 2) %>%
  kable_styling()

```


# Table 1

# --> ? add race, SES? 

```{r}
# Table1 tutorials: 
## https://cran.r-project.org/web/packages/table1/table1.pdf 
## https://cran.r-project.org/web/packages/table1/vignettes/table1-examples.html
 
# table labels
t1_labels <- list(
  labels = list(
    casi_irt = "CASI-IRT",
    visit_age = "Visit Age",
    year2 = "Calendar Year (2 yr Cat)",
    apoe = "APOE e4 Allele",
    male = "Sex",
    degree = "Degree",
    #race_white = "Race",
    variable = "Pollutant",
    #apoe_available = "Included in Main Analysis",
    #model_wt = "IPW for Modeling Cohort",
    high_exposure_PNC = "High PNC Exposure  (>Median)",
    #high_exposure_NO2 = "NO2 Above Median",
    #exposure_NO2 = "Residential NO2 (ppb) Exposure",
    exposure_PNC = "Residential PNC (pt/cm3) Exposure"
    ),
  units = list(
    visit_age = "Years"
     ),
  categoricals = list(
    apoe = list('1' = "Carriers",
                '0' = "Non-Carriers"),
    # apoe_available = list('TRUE' = "Included in Main Analysis",
    #                       'FALSE' = "Not Included in Main Analysis"),
    male = list('1' = "Male",
                '0' = "Female"),
     
        degree = list('0' = "None",
                  '1' = "GED/High School",
                  '3' = "Bachelor's",
                  '4' = "Master's",
                  '5' = "Doctorate",
                  '6' = "Other"),
    # race_white = list('1' = "White",
    #                   '0' = "People of Color"),

    # income_cat = list('1' = "<$35,000",
    #                   '2' = "$35,000 - <$50,000",
    #                   '3' = "$50,000 - <$75,000",
    #                   '4' = ">$75,000"),
    
    high_exposure_PNC = list('FALSE' = "PNC Below Median",
                                   'TRUE' = "PNC Above Median")
    # high_exposure_NO2 = list('FALSE' = "No",
    #                                'TRUE' = "Yes")
    ) 
  ) 

print("Baseline cohort characteristics stratified by whether 5-year PNC exposure at baseline was below or above the median.")
# Main Table 1
t1read(filter(pop), t1_labels) %>%
  table1(~ visit_age + male + year2 + casi_irt + apoe + degree + #race_white + 
           exposure_PNC  #exposure_NO2 + high_exposure_NO2 
           | high_exposure_PNC, data=.)

```

# Health Model Results

## Estimates 


# --> extended model rusults to beta plots. Main + race + SES? 
# --> ? somehow incorporate IQR into these plots??

tables include the proportion significant

```{r}
prop_sign <- model_coefs %>%
  group_by(variable, design, version) %>%
  summarize(prop_sign = mean(significant),
            sd = sd(est)
            )

coef_table <- model_coefs %>%
  group_by(variable, design, version) %>%
  alt_boxplot(var = "est") %>%
  left_join(prop_sign)

coef_table %>%
  filter(variable %in% main_pollutants_labels) %>%
  kable(caption = "Distribution of health effect estimates from each design, and the proportion of campaigns that produce significant findings", 
        digits = 3) %>%
  kable_styling()


#######################################
prop_sign %>%
  filter(variable %in% main_pollutants_labels,
         grepl("Total Stops|Seasons", design)
         ) %>%
  group_by(variable) %>%
  alt_boxplot(var = "prop_sign") %>%
  mutate_if(is.numeric, ~round(., 2)) %>%
  kable(caption = "Distribution of proportion of significant findings for fewer stops & seasons") %>%
  kable_styling()

#######################################
```

summary boxplots of betas 

```{r}
# comparison of all-data betas
model_coefs %>%
  filter(design == "All Data") %>% 
  mutate(
    variable = gsub("PNC, ", "", variable),
    variable = gsub(" nm.*", "", variable),
    variable = gsub("Total \\(pt/cm3\\)", "Total (10-420)", variable),
    
    variable = factor(variable, levels = c("12", "21", "27", "37", "49", "65", "87", "116", "154", "Total (10-420)"))
  ) %>%  

  ggplot(aes(x=variable, col=significant)) +  
  facet_wrap(~design+version) + 
  geom_hline(yintercept = 0, linetype=2, alpha=0.2) +
  geom_pointrange(aes(y=est, ymin=lower, ymax=upper), size=0.5, alpha=0.8) +
      labs(col = "Statistically Significant",
           x="Size-Specific PNC, nm",
           y = "Beta Estimate (per 1k pt/cm3)"
           )

```


The black horizontal line and gray area are the health effect estimate from the full campaign

```{r, fig.height=8, fig.width=8}
# x = main_pollutants_labels[2]
true_betas <- model_coefs %>%
  filter(design == "All Data") %>%
  select(variable, est, lower, upper, se)

true_betas %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  kable(caption = "beta estiamtes from the all data campaign") %>%
  kable_styling()

# x = all_pollutants_labels[1]
lapply(all_pollutants_labels, function(x){ 
    
      p <- model_coefs %>%
      filter(variable == x,
             design != "All Data") %>%
    
      ggplot(aes(x=campaign, col=significant)) +  #col=version
      facet_wrap(~design+version) + 
      geom_hline(yintercept = 0, linetype=2, #col="red", 
                 alpha=0.2) +
      geom_rect(inherit.aes = F, data=filter(true_betas, variable==x), aes(ymin = lower, ymax = upper, xmin=-Inf, xmax=Inf), alpha=0.25) +
      geom_hline(data=filter(true_betas, variable==x), aes(yintercept = est)) +
      geom_pointrange(aes(y=est, ymin=lower, ymax=upper), size=0.5, alpha=0.8) +
      labs(title=x, col = "Statistically Significant",
           x="Campaign No.",
           y = "Beta Estimate"
           )
      
      print(p)
  
      if(grepl("Total", x)) {
        fp <- image_path
        } else {
        fp <- file.path(image_path, "SI")
      }
      
  ggsave(file.path(fp, paste0("beta_", 
                                      #gsub("\\,.*| .*", "", x), 
                                      gsub(" \\(.*| nm.*", "", x), 
                                      ".png")), 
         width = 8, height = 8)
  
})

```




solid horizontal line is the estimate from the all-data campaign 

```{r}
model_coefs %>%
  filter(grepl("Total Stops|Seasons", design)) %>%
  group_by(variable) %>%
  alt_boxplot(var = "est") %>%
  kable(caption = "distribution of beta estimates for fewer stops & seasons", digits = 3) %>%
  kable_styling()


model_coefs %>%
  filter(design != "All Data") %>%
  ggplot(aes(x=version, y=est)) +
  facet_grid(variable~design, scales="free", switch="both") + 
  #geom_rect(inherit.aes = F, data=true_betas, aes(ymin = lower, ymax = upper, xmin=-Inf, xmax=Inf), alpha=0.25) +
  geom_hline(data=true_betas, aes(yintercept = est), linetype=1, alpha=0.5) +
  geom_hline(yintercept = 0, linetype=2, alpha=0.2) +
  
  geom_boxplot() + 
  labs(y = "Beta Estimate",
       x = "Design" #x = "Design-Version"
       )


```




## Beta bias

```{r}
bias0 <- model_coefs %>%
  group_by(variable) %>%
  mutate(ref = est[design == "All Data"],
         error = est - ref,
         error_pct = round(error/abs(ref)*100, 1)) %>%
  filter(design != "All Data",
         variable %in% main_pollutants_labels) 



bias <- bias0 %>%
  group_by(variable, design, version) %>%
  alt_boxplot(var = "error") 

bias %>% 
  kable(caption = "Distribution of beta errors for each design", 
        digits = 3) %>%
  kable_styling()

#######################################
bias0 %>%
  filter(grepl("Total Stops|Seasons", design)) %>%
  alt_boxplot(var = "error") %>%
                        # rounding impacts % error estimate (14 vs 17%)
  mutate_if(is.numeric, ~round(., 3)) %>% 
  kable(caption = "Distribution of beta errors for fewer stops & seasons") %>%
  kable_styling()

bias0 %>%
  filter(grepl("Fewer Hours", design)) %>%
  alt_boxplot(var = "error") %>%
  mutate_if(is.numeric, ~round(.,3)) %>%
  kable(caption = "Distribution of beta errors for fewer hours") %>%
  kable_styling()
#######################################

#bias %>%
bias0 %>%
  ggplot(aes(x=version, 
             y=error
             )) +
  facet_grid(variable~design, scales = "free", switch="both") +
  geom_hline(yintercept = 0, linetype=2, alpha=0.5) + 
  geom_boxplot()+
  labs(y = "Beta Error",
       x = "Design" #x = "Design-Version"
       )
  

ggsave(file.path(image_path, "bias.png"), width = 6, height = 6)


```


Percent error in the estimated betas (n=30 campaign models for each design-version)

```{r}

bias_pct <- bias0 %>%
  group_by(variable, design, version) %>%
  alt_boxplot(var = "error_pct") 

bias_pct %>% 
  #select(-c(Qmin, Qmax)) %>%
  mutate_if(is.numeric, ~round(.)) %>%
  kable(caption = "Distribution of beta errors (%) for each design") %>%
  kable_styling()


#######################################
bias0 %>%
  filter(grepl("Total Stops|Seasons", design)) %>%
  alt_boxplot(var = "error_pct") %>%
  mutate_if(is.numeric, ~round(.)) %>%
  kable(caption = "Distribution of beta errors (%) for fewer stops & seasons") %>%
  kable_styling()

bias0 %>%
  filter(grepl("Fewer Hours", design)) %>%
  alt_boxplot(var = "error_pct") %>%
  mutate_if(is.numeric, ~round(.)) %>%
  kable(caption = "Distribution of beta errors (%) for fewer hours") %>%
  kable_styling()
#######################################


#bias_pct %>%
bias0 %>%
  ggplot(aes(x=version, y=error_pct)) +
  facet_grid(variable~design, scales = "free", switch="both") +
  geom_hline(yintercept = 0, linetype=2, alpha=0.5) + 
  geom_boxplot(
    #aes(ymin = Qmin, lower = Q25, middle = Q50, upper = Q75, ymax = Qmax), stat = "identity"
    ) +
  # scale_y_continuous(sec.axis = sec_axis(~./unique(bias0$ref[1]), 
  #                                        name="Beta Error"))+
 
  labs(y = "Beta Error (%)",
       x = "Design" #x = "Design-Version"
       )
  

ggsave(file.path(image_path, "bias_pct.png"), width = 6, height = 6)

```


## SD of Betas 

N = 30 campaigns per design-version

```{r}
model_coefs %>%
  filter(design != "All Data",
         variable %in% main_pollutants_labels
         ) %>%
  group_by(variable, design, version) %>%
  summarize(N = n(),
            SD_of_betas = sd(est)) %>%
  
  ggplot(aes(x=version, y=SD_of_betas)) + 
  facet_grid(variable~design, scales = "free", switch="both") + 
  geom_point() + 
  labs(y = "SD of Beta Estimates",
       x = "Design" #x = "Design-Version"
       )
   

ggsave(file.path(image_path, "SI", "sd_of_betas.png"), width = 5, height = 5)

```

## Beta SEs 

```{r}

model_coefs %>%
  filter(design != "All Data",
         variable %in% main_pollutants_labels
         ) %>%
  
  ggplot(aes(x=version, y=se)) +
  facet_grid(variable~design, scales = "free") +
  geom_hline(data=filter(true_betas, variable %in% main_pollutants_labels), 
             aes(yintercept = se), alpha=0.5, linetype=2) +
  geom_boxplot() + 
  labs(col = "Statistically\nSignificant", y="Beta SE")
  
  ggsave(file.path(image_path, "SI", "se.png"), width = 6, height = 6)

```



# Appendix
## Inclusion/exclusion table

```{r}
# https://cran.r-project.org/web/packages/PRISMAstatement/vignettes/exclusionflowcharts.html 

# --> last row looks weird

print("persons")

flow_exclusions(
  incl_counts = exclusion_table$persons,
  total_label = "Full Cohort",
  incl_labels = exclusion_table$description[2:length(exclusion_table$description)],
  percent_of_total = T,
  format_args = list(big.mark  = ",")
  )


print("person-years")

flow_exclusions(
  incl_counts = exclusion_table$person_years,
  total_label = "Full Cohort",
  incl_labels = exclusion_table$description[2:length(exclusion_table$description)],
  percent_of_total = T,
  format_args = list(big.mark  = ",")
  )

```




