---
title: "Epi Results using LCM Exposure Models"
author: "Magali Blanco"
date: ' `r Sys.time()` '
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    number_sections: true
    toc_float: true
    collapsed: false
    smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

# Setup 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, 
                      cache=F, cache.comments = F, 
                      message = F, warning = F, 
                      tidy.opts=list(width.cutoff=60), tidy=TRUE#, fig.height = 10, fig.width = 10
                      )  

# Clear workspace of all objects and unload all extra (non-base) packages
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
           detach, character.only=TRUE, unload=TRUE, force=TRUE))}

pacman::p_load(tidyverse, kableExtra)    

dt_path <- file.path("Output", readRDS(file.path("Output", "latest_dt_version.rda")))

set.seed(1)

source("functions.R")
output_data_path <- file.path(dt_path, "epi", "20241108" #"20240725"
                              )

image_path <- file.path("..", "Manuscript", "Images", "v5", "other", "lcm")
if(!dir.exists(image_path)) {dir.create(image_path, recursive = T)}
# ggplot settings
theme_set(theme_bw())
theme_update(legend.position = "bottom")

##################################################################################################
# LOAD DATA
##################################################################################################
# reference models
## stataionary and LCM
st_ref_model <- "full_ST" #ST 
sp_ref_model <- "full_SP" # SP 
## no LCM
st_ref_model2 <- "fptv_no" #ST 
sp_ref_model2 <- "fp_no" # SP 

cw <- read.csv(file.path(dt_path, "model_cw_lcm.csv")) %>%
  mutate(model = gsub("pm25_", "", model))

# person-level exposures 
cs <- readRDS(file.path(output_data_path, "dt_for_cross_sectional_analysis_lcm.rda")) %>%
  rename(exposure = avg_0_5_yr) %>%  
  select(-starts_with("avg_")) %>%
  # note that I didn't do anything to update NO2 labels
  mutate(model = gsub("pm25_", "", model),
         model = gsub("no2_SP_", "no2", model),
         ) %>%
  left_join(select(cw, model, model_type)) %>%
  #drops 1 person that the "full" model has missing values for
  drop_na(exposure)


# health effect estimates & CW
model_coefs <- readRDS(file.path(output_data_path, "model_coefs_lcm.rda")) %>%
  
  mutate(#model_type = ifelse(grepl("_SP", model), "SP", "ST"),
         
         variable= ifelse(grepl("no2", model), "NO2", "PM2.5"),  
         model = gsub("pm25_", "", model),
         model = gsub("no2_SP_", "no2", model),
         model = as.factor(model),
         ref_model = ifelse(model %in% c(st_ref_model, sp_ref_model, "no22_1", "no2_SP_2_1"), "Full Model", "Alternative LCM Model"),
         ref_model = factor(ref_model, levels=c("Full Model", "Alternative LCM Model"))) %>%
  left_join(cw) 

#model_coefs$model

# quick fix for NO2 - has formatting issues otherwise
model_coefs_no2 <- readRDS(file.path(output_data_path, "model_coefs_lcm.rda")) %>%
  filter(grepl("no2", model)) %>%
  mutate(model_type = ifelse(grepl("_SP", model), "SP", "ST"),
         method = ifelse(grepl("2_1", model), "With LCM",
                         ifelse(grepl("6_1", model), "No LCM", NA)),
         method = factor(method, levels=c("With LCM", "No LCM")),
         ref_model = ifelse(model %in% c(st_ref_model, sp_ref_model, "no22_1", "no2_SP_2_1"), "Full Model", "Alternative LCM Model"),
         ref_model = factor(ref_model, levels=c("Full Model", "Alternative LCM Model"))
         )



```

# Model definitions


```{r}
model_coefs %>%
  mutate(model = gsub("fp_|rp_|fptv_|_SP|_ST", "", model)) %>%
  group_by(Label=model, Description=method,# variable
           ) %>% 
  summarize(model_type = paste(unique(model_type), collapse = ", ")) %>%
  arrange(Label) %>%
  kable() %>% 
  kable_styling()

```

# Model R2

JB should have this.

# Participant Exposure Predictions 

comparison of predicted 5 yr exposures at baseline

```{r}
# plot
st_cs <- cs %>%
  filter(model_type=="ST") %>%
  select(-c(exp_coverage, exact_coverage, imp_coverage, imputation_quality)) %>%
  pivot_wider(names_from = model, values_from = exposure) %>%  
  rename(full_model = st_ref_model) %>%  
  pivot_longer(cols = starts_with(c("fptv_")))
  
sp_cs <- cs %>%
  filter(model_type=="SP") %>%
  select(-c(exp_coverage, exact_coverage, imp_coverage, imputation_quality)) %>%
  pivot_wider(names_from = model, values_from = exposure) %>%
  rename(full_model = sp_ref_model) %>%  
  pivot_longer(cols = starts_with(c("fp_", "rp_")))
  
print("the full model is our default epi model with stationary and LCM")
# rbind(st_cs, sp_cs) %>%
#   mutate(name = gsub("fp_|rp_|fptv_|_SP|_ST", "", name)) %>%
#   ggplot(aes(x=full_model, y=value, col=name)) +
#   facet_wrap(~model_type, scales="free") +
#   geom_point(alpha=0.05) +
#   geom_smooth() +
#   geom_abline(slope = 1, intercept = 0, linetype=2) + 
#   labs(col="LCM Model", y="LCM Model Prediction", x= "Full ST PM2.5 Model Prediction")
# 
# ggsave(file.path(image_path, "5yr_exposure_comparisons.png"), width = 8, height = 6)

#table
cs %>%
  group_by(model, model_type) %>%
  alt_boxplot(var="exposure") %>%
  rename(Q2.5=Qmin, Q97.5=Qmax) %>%
  kable(caption = "Distribution of PM2.5 ug/m3) predictions", 
        digits = 0, format.args = list(big.mark=",")) %>% 
  kable_styling()

```

**Correlations**: exposure predictions from all models generate highly correlated predictions

# --> is this right? some correlations are 1.0, most are very low 

```{r}
comparison_models <- setdiff(unique(cs$model), st_ref_model) %>% setdiff("full_SP")

# cs %>%
#   select(study_id, exposure, model) %>%
#   filter(model != sp_ref_model) %>%
#   pivot_wider(names_from = model, values_from = exposure) %>%  
#   pivot_longer(cols = comparison_models) %>%  
#   # 1 person doesn't have ST full predictions
#   drop_na(st_ref_model) %>%
#   group_by(name) %>% 
#   summarize(correlation = cor(get(st_ref_model), value)) %>%
#   kable(caption = "Correlation (R) of fptv_no predictions with predictions from other methods", 
#         digits = 2, 
#         col.names = c("Model", "Correlation with fptv_no")) %>%
#   kable_styling()

```

# Comparison of health effect estimates (CASI-IRT)

## PM2.5 

the resulting health estimates from using UK-PLS and various ML UFP exposure models is similar, with random forests & spatcv being the most different (~25-35% lower point estimate)

```{r}
ref_beta <- model_coefs$est[model_coefs$model==st_ref_model]

print("adjustd association between P-TRAK UFP (1k pt/cm3) and CASI-IRT")
model_coefs %>%
  filter(variable=="PM2.5") %>%
    mutate(model = gsub("fp_|rp_|fptv_|_SP|_ST", "", model)) %>%

  ggplot(aes(y=model, col=ref_model)) +  
  facet_grid(cols = vars(model_type), scales = "free_y", switch = "y", space="free") +
  geom_vline(xintercept = ref_beta, linetype=1, alpha=0.5) +
  geom_vline(xintercept = 0, linetype=2, alpha=0.2) +
  geom_pointrange(aes(x=est, xmin=lower, xmax=upper), size=0.5, alpha=0.8, orientation = "y") +
  scale_x_continuous(sec.axis = sec_axis(
    trans=~(.-ref_beta)/-ref_beta, name="% Difference from Full ST Model", labels = scales::percent, breaks = c(-1.5,0, 1.5)), breaks = c(-0.06, -0.03, 0, 0.03)) +
  labs(col = NULL,
           y="LCM Model",
           x = "Coefficient Estimate (95% CI)")

ggsave(file.path(image_path, "pm25_health_estimate.png"), width = 8, height = 6)

```

## NO2

```{r}
ref_beta <- model_coefs_no2$est[model_coefs_no2$model=="no22_1"] #ST no22_1

model_coefs_no2 %>%
    filter(
           model %in% c("no22_1", "no2_SP_2_1", # with LCM ##gold w/o historical - all monitors, ST & SP models #UPDATED Jul 2024
                        "no26_1", "no2_SP_6_1" # no LCM  ##no homes - AQS + 3 snapshot
                        )) %>%
  

  ggplot(aes(#y=model, 
             y=method, 
             col=ref_model)) +  
  facet_grid(cols = vars(model_type), scales = "free_y", switch = "y", space="free") +
  geom_vline(xintercept = ref_beta, linetype=1, alpha=0.5) +
  geom_vline(xintercept = 0, linetype=2, alpha=0.2) +
  geom_pointrange(aes(x=est, xmin=lower, xmax=upper), size=0.5, alpha=0.8, orientation = "y") +
  # scale_x_continuous(sec.axis = sec_axis(
  #   trans=~(.-ref_beta)/-ref_beta, name="% Difference from Full ST Model", labels = scales::percent, 
  #   #breaks = c(-1.5,0, 1.5)
  #   ), 
  #   #breaks = c(-0.06, -0.03, 0, 0.03)
  #   ) +
  labs(col = NULL,
           y="LCM Model",
           x = "Coefficient Estimate (95% CI)")

ggsave(file.path(image_path, "no2_health_estimate.png"), width = 8, height = 6)


```


