---
title: "Epi Results using Onroad Exposure Models"
author: "Magali Blanco"
date: ' `r Sys.time()` '
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    number_sections: true
    toc_float: true
    collapsed: false
    smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

# --> update file paths 

# Setup 

```{r setup, include=FALSE}
# Rscript -e 'rmarkdown::render("9_road_summary.Rmd", "html_document")'
knitr::opts_chunk$set(echo = F, 
                      cache=F, cache.comments = F, 
                      message = F, warning = F, 
                      tidy.opts=list(width.cutoff=60), tidy=TRUE)  

# Clear workspace of all objects and unload all extra (non-base) packages
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
           detach, character.only=TRUE, unload=TRUE, force=TRUE))}

pacman::p_load(tidyverse, kableExtra, ggpubr, sf, ggspatial)    # ggpubr::ggarange()

dt_path <- file.path("Output", readRDS(file.path("Output", "latest_dt_version.rda")))

set.seed(1)

source("functions.R")
output_data_path <- file.path(dt_path, "epi", "20240725")

image_path <- file.path("..", "Manuscript", "Images", "v5", #"v4", 
                        "other", "road")
if(!dir.exists(image_path)) {dir.create(image_path, recursive = T)}
if(!dir.exists(file.path(image_path, "SI"))) {dir.create(file.path(image_path, "SI"), recursive = T)}
if(!dir.exists(file.path(image_path, "presentations"))) {dir.create(file.path(image_path, "presentations"), recursive = T)}
# ggplot settings
theme_set(theme_bw())
theme_update(legend.position = "bottom")

##################################################################################################
# FUNCTIONS
##################################################################################################
# fn to recode onroad data
design_levels <- c("Balanced", "Random Segments", "Random Clusters", "Sensible Clusters", "Unsensible Clusters", "Road Type", "Route")

recode_onroad_dt <- function(dt) {
  dt %>%
    mutate(
      #spatial = ifelse(spatial_code=="sn", "Non-spatially Dependent Sampling", "Spatially Unbalanced Sampling"),
      # spatial = ifelse(design %in% c("road_type", "sensible", "unsensible") | , 
      #                  
      #                  "Non-spatially Dependent Sampling", "Spatially Unbalanced Sampling"),
      
      
      visits = str_extract(visits, "\\d+"),
      version = ifelse(adjusted=="adjusted", paste(version, "plume adj"), version),
      version = gsub("hours", "hr", version),
      version = gsub("business", "bus", version),
      version = str_to_title(version),
      #version = factor(version, levels = version_levels),
      version = factor(version, levels = sort(unique(version))),
      design = case_when(
        design=="balanced" ~ "balanced",
        design=="unbalanced" ~ "random segments",
        design=="random" ~ "random clusters",
        design=="sensible" ~ "sensible clusters",
        design=="unsensible" ~ "unsensible clusters",
        design=="road_type" ~ "road type",
        design=="route" ~ "route",
         ),
      design = str_to_title(design),
      design = factor(design, levels = design_levels),
      adjusted = str_to_title(adjusted)
      ) 
  
}
##################################################################################################
summary_table <- function(df, var){
  df <- df %>%
    rename(var = all_of(var)) %>%
    
    #calculate quantiles
    summarize(
      N = n(),
      Min = min(var),
      Q05 = quantile(var, 0.05),
      Q10 = quantile(var, 0.10),
      Q25 = quantile(var, 0.25),
      Q50 = quantile(var, 0.50),
      Q75 = quantile(var, 0.75),
      Q90 = quantile(var, 0.90),
      Q95 = quantile(var, 0.95),
      Max = max(var)
    )
  
  names(df)[names(df)==var] <- var
  
  return(df) 
  
}
##################################################################################################
# LOAD DATA
##################################################################################################
# raw mobile data
#cov <- readRDS(file.path("data", "onroad", "annie", "cov_onroad_preprocessed.rds")) #%>% pull(native_id)
project_crs <- 4326  #lat/long
m_crs <- 32148

clusters <- readRDS(file.path("data", "onroad", "annie", "segment_clusters_updated.rds")) %>%
  select(-c(latitude, longitude)) %>%
  # drop annie's old clusters for now
  filter(cluster_type != "cluster3")

cov <- readRDS(file.path("data", "onroad", "dr0364d_20230331_modified.rda")) %>%
  st_as_sf(coords = c('longitude', 'latitude'), crs=project_crs, remove = F) %>%
  st_transform(m_crs)  
  
onroad_cov <- cov %>%
  # add cluster IDs
  left_join(clusters, by = c("location" = "id")) %>%
  select(location, cluster_type, #cluster, 
         everything())

saveRDS(onroad_cov, file.path("data", "onroad", "dr0364d_20230331_modified_with_clusters.rda"))

# crosswalks
cw <- read.csv(file.path(dt_path, "onroad", "onroad_model_cw.csv")) %>%
  # drop annie's old clusters for now
  filter(!grepl("_c3_", model)) %>%
  mutate(variable="pnc_noscreen") %>%
  recode_onroad_dt() %>%
  label_pollutants() 

stationary_cw <- read.csv(file.path(dt_path, "model_cw.csv")) %>%
  filter(variable =="pnc_noscreen",
         design == "full") %>% 
  label_pollutants()  %>%
  mutate(visits = "29",
         adjusted = "Unadjusted",
         #spatial = "Reference"
         )

cw2 <- bind_rows(cw, stationary_cw) %>%
  select(model, campaign, version, design, visits, adjusted, #spatial
         )

#model eval
eval_files <- list.files(file.path(dt_path, "onroad", "model_eval")) %>% str_subset(".rda")

model_eval <- lapply(eval_files, function(x){
  readRDS(file.path(dt_path, "onroad", "model_eval", x)) %>%
    # drop annie's old clusters for now
    filter(!grepl("_c3_", model)) %>%
    left_join(select(cw, #spatial, 
                    design, version, visits, adjusted, campaign, model), by="model") 
  }) %>%
  bind_rows()
  
stationary_model_eval <- readRDS(file.path(dt_path, "model_eval.rda")) %>%
  filter(reference == "gs_estimate",
         model %in% stationary_cw$model)  

#ref health estimates from stationary models & extended health analyses
ref_model_coefs <- readRDS(file.path(output_data_path, "model_coefs_extended.rda" #"model_coefs.rda"
                                     )) %>%
  filter(model=="s_pncnoscreen_all_01") %>%
  left_join(select(stationary_model_eval, model, reg_based_R2), by="model")
 
tot_pnc <- filter(ref_model_coefs, model=="s_pncnoscreen_all_01") %>% pull(est)

# person-level exposures 
stationary_cs <- readRDS(file.path(output_data_path, "dt_for_cross_sectional_analysis.rda")) %>%
  rename(exposure = avg_0_5_yr) %>%  
  select(-starts_with("avg_")) %>%
  right_join(stationary_cw)

cs <- readRDS(file.path(output_data_path, "dt_for_cross_sectional_analysis_road.rda")) %>%
  rename(exposure = avg_0_5_yr) %>%  
  select(-starts_with("avg_")) %>%
  right_join(cw) %>%
  bind_rows(stationary_cs)

# health effect estimates & CW
model_coefs <- readRDS(file.path(output_data_path, "model_coefs_road_extended.rda" #"model_coefs_road.rda"
                                 )) %>%
  right_join(cw, by="model") %>%
  #filter(model %in% cw$model) %>%
  mutate(variable="pnc_noscreen",
         pct_difference = (est-tot_pnc)/tot_pnc*100#-tot_pnc*100
         )  

# onroad model predictions at stationary locations
stationary_prediction_files <- list.files(file.path(dt_path, "onroad", "model_eval", "predictions_at_stationary_sites"))

onroad_predictions <- lapply(stationary_prediction_files, function(x){
  readRDS(file.path(dt_path, "onroad", "model_eval", "predictions_at_stationary_sites", x))
}) %>%
  bind_rows() %>% 
  right_join(cw, by="model")

all_predictions <- readRDS(file.path(dt_path, "UK Predictions", "all_predictions.rda")) %>%
  filter(design == "full",
         variable == "pnc_noscreen") %>%
  mutate(model = "s_pncnoscreen_all_01",
         visits = "29", #as.character(visits)
         version = "All Hr") %>%
  left_join(select(stationary_cw, variable, design, model)) #%>%
  # select(names(onroad_predictions)) %>%
  # bind_rows(onroad_predictions) %>% 

all_predictions <- bind_rows(onroad_predictions, all_predictions) #%>%
  #mutate(version = factor(version, levels = c("All Hr Plume Adj", "All Hr", "Bus Hr Plume Adj", "Bus Hr")),)


# --> ERROR W/ LABEL MERGING  

  #left_join(cw2)
  # left_join(
  #   bind_rows(cw, stationary_cw) %>%
  #             select(model, design, version, campaign, visits, adjusted, spatial) %>% View()
  #           )

# reference P-TRAK data - number of visits (stops) per site; for the HEI dataset (not necessarily the "true" health models)
stops_w <- readRDS(file.path(dt_path, "stops_used.rda"))

##################################################################################################
# COMMON VARIABLES
##################################################################################################
#spatial_names <- unique(model_eval$spatial)
version_levels <- unique(cw$version)

```

# reference stationary P-TRAK data

```{r}

stops_w %>%
  drop_na(pnc_noscreen) %>%
  group_by(location) %>%
  summarize(visits = n()) %>%
  summarize(
    min = min(visits),
    q25 = quantile(visits, 0.25),
    mean = mean(visits),
    q50 = quantile(visits, 0.50),
    max=max(visits)
  )%>%
  kable(caption = "distribution of visits per stop with unscreened P-TRAK readings") %>%
  kable_styling()

```


# mobile data

```{r}
# onroad_cov %>%
#   st_drop_geometry() %>%
#   group_by(cluster_type) %>%
#   summarize(
#     locations = length(unique(location)),
#     #clusters = length(unique(cluster_type)),
#      #mean_segments_per_cluster
#   ) %>%
#   kable(caption = "onroad segments and spatial clusters used") %>%
#   kable_styling()

```

## map

# --> ? add background map? 
Brian's example: https://github.com/brianhigh/test_stopr/blob/main/test_stopr.md 

```{r}
 
onroad_cov %>%
  #mutate(cluster = as.factor(cluster_type)) %>%
  ggplot(aes(col=cluster_value), ) +
  facet_wrap(~cluster_type) + 
  geom_sf(size=0.5, show.legend=F) +
  
  # add scale & N arrow to top rught
  annotation_scale(location = "tr") +
  annotation_scale(location = "tr", unit_category ="imperial", pad_y = unit(0.55, "cm")) +
  annotation_north_arrow(location = "tr", pad_y = unit(0.5, "in"), style = north_arrow_fancy_orienteering) +
  
  theme_bw() + 
  theme(# remove the vertical grid lines
        panel.grid.major = element_blank()) + 
  scale_color_viridis_c()

ggsave(file.path(image_path, "SI", "cluster_map.png"), width = 4, height = 8)

```





# Design definitions


```{r}
t1_a <- cw %>%
  distinct(spatial, version, design, visits, adjusted) %>% 
  filter(grepl("non-spatial", spatial, ignore.case=T)) %>%
  mutate(version = gsub(" Plume Adj", "", version),
         adjusted = ifelse(adjusted == "adjusted", "Plume Adjusted", "Unadjusted")) %>%
  group_by(spatial) %>%
  summarize(
    version = paste(unique(version), collapse=", "),
    visits = paste(unique(visits), collapse=", "),
    design = paste(unique(design), collapse=", "),
    adjusted = paste(unique(adjusted), collapse=", "),
  ) 

t1_b <- cw %>%
  distinct(spatial, version, design, visits, adjusted) %>% 
  filter(!grepl("non-spatial", spatial, ignore.case=T)) %>%
  mutate(version = gsub(" Plume Adj", "", version),
         adjusted = ifelse(adjusted == "adjusted", "Plume Adjusted", "Unadjusted")) %>%
  group_by(spatial) %>%
  summarize(
    version = paste(unique(version), collapse=", "),
    visits = paste(unique(visits), collapse=", "),
    design = paste(unique(design), collapse=", "),
    adjusted = paste(unique(adjusted), collapse=", "),
  ) 

rbind(t1_a, t1_b) %>%
  rename_all(~str_to_title(.)) %>%
  kable(caption = "Onroad sampling designs. Balanced sampling occurs when all sites receive the same number of visits, either 4 or 12. Unbalanced sampling occurs when sites receive a different number of visits, sampled on a log-normal distribution with median of 4 or 12 visits.") %>% 
  kable_styling()

```

# Annual average estimates

```{r}
# table/boxplots of distribution
estimates <- all_predictions %>%
  filter(grepl("^s_", model)) %>%
  distinct(location, gs_estimate, prediction
           #spatial, 
           #adjusted, design, version, visits
           ) %>% 
   # --> why have to do this??
  drop_na() %>% 
  
  pivot_longer(cols = c(gs_estimate, prediction)) %>% 
  group_by(name) %>%
  summary_table(var = "value") 

estimates %>%
  kable(caption = "Distribution of estimated and all-data stationary model predicted annual average PNC at 309 stationary locations", 
      digits = 0,
      format.args = list(big.mark=",")
      ) %>%
kable_styling()


predicted <- all_predictions %>%
  filter(grepl("^r_", model)) %>%
  left_join(cw) %>%  
  group_by(spatial, adjusted, design, version, visits) %>%   
  
   # --> why have to do this??
  #drop_na(prediction) %>%
  
  summary_table(var = "prediction") 

bind_rows(#estimates,
      predicted) %>%
  select(names(predicted)) %>%
kable(caption = "Distribution of estimated and predicted annual average PNC at 309 stationary locations", 
      digits = 0,
      format.args = list(big.mark=",")
      ) %>%
kable_styling()


########################################################################################
# plot

ref_prediction_distribution <- all_predictions %>%
  filter(model == ref_model_coefs$model) %>%
  summarize(n=n(),
            median = median(prediction),
            q25 = quantile(prediction, 0.25),
            q75 = quantile(prediction, 0.75)
            )  

print("dashed line is median (IQR) predicted PNC from the all-data stationary model")
all_predictions %>%
  filter(model != ref_model_coefs$model) %>%
  mutate(visits = paste(visits, "visits"),
         #visits = factor(visits, levels = c("29 visits", "12 visits", "4 visits"))
         design = factor(design, levels = design_levels)
         ) %>%
  
  group_by(version, design, visits) %>%
  summary_table(var = "prediction") %>%
  
  ggplot(aes(x=version, fill=design)) +
  #ggplot(aes(y=prediction, x=version, fill=design)) +
  facet_grid(rows = vars(visits), switch = "both") +
  #geom_boxplot(position = "dodge") +
  geom_boxplot(position = "dodge", stat="identity", aes(ymin=Q10, lower=Q25, middle=Q50, upper=Q75, ymax=Q90)) +
  geom_hline(yintercept = ref_prediction_distribution$median, linetype=2, alpha=0.5) +
  geom_hline(yintercept = c(ref_prediction_distribution$q25, ref_prediction_distribution$q75), linetype=3, alpha=0.3) +

  labs(x = "Version", y = "Predicted PNC (pt/cm3)", fill="Location Visit\nSelection")

ggsave(file.path(image_path, "SI", "predicted_ufp_309_sites.png"), width = 8, height = 8)

```


# Model R2

model eval is at 309 stationary sites


results           
* BH unadjusted R2 are all 0     
* All hours unadju are all 0 except for 1 value

# --> ADD pct difference variable

```{r, fig.height=8, fig.with=8}
# # OLD
# # x = spatial_names[2]
# lapply(spatial_names, function (x) {
#   p <- model_eval %>%
#     filter(spatial==x) %>%  
#     mutate(visits = paste(visits, "visits")) %>%
#   ggplot(aes(y=MSE_based_R2, x=version, fill=design)) + 
#   geom_boxplot(position = "dodge")  +
#     #geom_point(position = "dodge", aes(col=design)) +
#   labs(y = "MSE-based R2")
# 
#   if(grepl("non-spatial", x, ignore.case = T)) {
#     p <- p+ labs(fill = "Visits are") +
#       #facet_wrap(~spatial+visits, ncol = 1)
#       facet_grid(rows = vars(visits), cols = vars(spatial),  switch = "both")
#   } else {
#     p <- p + labs(fill = "Unbalanced Sampling") +
#       #facet_wrap(~spatial+visits, ncol = 1)
#       facet_grid(rows = vars(visits), cols = vars(spatial),  switch = "both")
#     }
#   }) %>%
#   ggarrange(plotlist = ., ncol = 1, heights = c(1.7,1) #, nrow=2, widths = c(1, 0.5)
#             )

stationary_r2_mse_ref <- ref_model_coefs$MSE_based_R2

print(paste("reference model R2 is the all-data stationary model:", round(stationary_r2_mse_ref, 2)))
model_eval %>%
  mutate(visits = paste(visits, "visits")) %>%
  
  group_by(version, design, visits) %>%
  summary_table(var = "MSE_based_R2") %>%

  ggplot(aes(x=version, fill=design)) +
  facet_grid(rows = vars(visits), switch = "both") +
  geom_boxplot(position = "dodge", stat="identity", aes(ymin=Q10, lower=Q25, middle=Q50, upper=Q75, ymax=Q90)) +
  
  #ggplot(aes(y=MSE_based_R2, x=version, fill=design)) +
  geom_hline(yintercept = stationary_r2_mse_ref, linetype=2, alpha=0.5) +
  #geom_boxplot(position = "dodge")  +
  scale_y_continuous(sec.axis = sec_axis( trans=~./stationary_r2_mse_ref, name="Proportion of Reference Model R2") ) +
  labs(y = "MSE-based R2") +
labs(fill = "Location Visit\nSelection")  

ggsave(file.path(image_path, "r2_mse.png"), width = 8, height = 6)

stationary_r2_reg_ref <- ref_model_coefs$reg_based_R2
print(paste("reference model R2 is the all-data stationary model:", round(stationary_r2_reg_ref, 2)))
model_eval %>%
  mutate(visits = paste(visits, "visits")) %>%
  
  group_by(version, design, visits) %>%
  summary_table(var = "reg_based_R2") %>%
  ggplot(aes(x=version, fill=design)) +
  facet_grid(rows = vars(visits), switch = "both") +
  geom_boxplot(position = "dodge", stat="identity", aes(ymin=Q10, lower=Q25, middle=Q50, upper=Q75, ymax=Q90)) +
  
  # ggplot(aes(y=reg_based_R2, x=version, fill=design)) +
  # facet_grid(rows = vars(visits), switch = "both") +
  geom_hline(yintercept = stationary_r2_reg_ref, linetype=2, alpha=0.5) +
  #geom_boxplot(position = "dodge")  +
  scale_y_continuous(sec.axis = sec_axis( trans=~./stationary_r2_reg_ref, name="Proportion of Reference Model R2") ) +
  labs(y = "Regression-based R2") +
labs(fill = "Location Visit\nSelection") 

ggsave(file.path(image_path, "SI", "r2_reg.png"), width = 8, height = 6)


```

# Participant Exposrue Predictions 

comparison of predicted 5 yr exposures at baseline

```{r, fig.height=8, fig.with=10}
# reference design
ref_cs <- cs %>%
  filter(
    model %in% ref_model_coefs$model
    # design=="Balanced",
    # version == "All Hr Plume Adj",
    # visits==12
    ) 

ref_cs %>%# View()
  summarize(
    N = n(),
    Participants = length(unique(study_id)),
    Campaigns = length(unique(campaign)),
    Min = min(exposure),
    Q05 = quantile(exposure, 0.05),
    Q25 = quantile(exposure, 0.25),
    Q50 = quantile(exposure, 0.50),
    Q75 = quantile(exposure, 0.75),
    Q95 = quantile(exposure, 0.95),
    Max = max(exposure)) %>%
  kable(caption = "Distribution of Predicted UFP (pt/cm3) exposure from the reference All data stationary exposure model", digits = 0, format.args = list(big.mark=",")) %>%
  kable_styling()


ref_cs_distribtuion <- ref_cs  %>%
  summarize(n = n(),
            median = median(exposure),
            q25 = quantile(exposure, 0.25),
            q75 = quantile(exposure, 0.75)
            )  
# plot
print("dashed lines are the median (IQR) predicted PNC for participants from the all-data stationary model")
cs %>%
  filter(!model %in% ref_model_coefs$model) %>%
  mutate(visits = paste(visits, "visits"),
         design = factor(design, levels = design_levels),
         version = factor(version, levels = version_levels),
         ) %>%
  
  group_by(version, design, visits) %>%
  summary_table(var = "exposure") %>%
   
  ggplot(aes(x=version, fill=design)) +
  geom_boxplot(position = "dodge", stat="identity", aes(ymin=Q10, lower=Q25, middle=Q50, upper=Q75, ymax=Q90)) +
  facet_wrap(~visits, scales="free_x", ncol = 1) +
  geom_hline(yintercept = ref_cs_distribtuion$median, linetype=2, alpha=0.5) +
  geom_hline(yintercept = c(ref_cs_distribtuion$q25, ref_cs_distribtuion$q75), linetype=3, alpha=0.3) +
  labs(fill="Location Visit\nSelection",
       y = "Predicted PNC (pt/cm3)"
       )  

ggsave(file.path(image_path, "SI", "cohort_5yr_exposure_comparisons.png"), width = 8, height = 8)

```


# Health effect estimates (CASI-IRT)

```{r}
ref_model_coefs %>%
  select(model, est, lower, upper, MSE_based_R2, reg_based_R2) %>%
  kable(caption = "health estimate from the reference all-data stationary exposure model", 
        digits = 3) %>%
  kable_styling()

```

```{r, fig.height=10, fig.with=10}
 temp <- data.frame(version=2.5,
                   label = c("Reference", "No Association"),
                   est=c(tot_pnc, 0),
                   design = NA,
                   visits = "4 visits")  #%>%
 # mutate(version = factor(version, levels = levels(model_coefs$version)))


 model_coefs %>%
  mutate(visits = paste(visits, "visits")) %>%  
  
  group_by(version, design, visits) %>%
  summary_table(var = "est") %>%
  ggplot(aes(x=version, fill=design)) +
  facet_grid(rows = vars(visits), switch = "both") +
  geom_boxplot(position = "dodge", stat="identity", aes(ymin=Q10, lower=Q25, middle=Q50, upper=Q75, ymax=Q90)) +
  geom_hline(yintercept = ref_model_coefs$est, linetype=2, alpha=0.5) +
  geom_hline(yintercept = 0, linetype=4, alpha=0.2) +
  #geom_text(aes(x=Inf, y=-0.019, label = "Reference Health Estimate"), hjust=1, vjust=1, size=3) +
  scale_y_continuous(sec.axis = sec_axis(trans=~(.-ref_model_coefs$est)/-ref_model_coefs$est, name="Health Point Estimate % Difference", labels = scales::percent),
                     # switch axes for visualization
                     position="right") +
   geom_label(data=temp, aes(y=est, label=label), fill= "white",show.legend = F, size=5) +

  labs(y = "Health Point Estimate",
       fill="Location Visit\nSelection",  
       x = "Version"
       )
 
ggsave(file.path(image_path, "ufp_health_estimate.png"), width = 8, height = 6)

```

## presentation

```{r}
# ref is stationary P-TRAK data
temp <- data.frame(version=2.5, 
                   label = c("All-Data Reference", "No Association"),
                   est=c(ref_model_coefs$est, 0),
                   design = NA,
                   visits = "~4 visits per location")  

##################################################################
model_coefs %>%
  filter(visits==4,
         design != "Unbalanced") %>%  
  mutate(visits = paste0("~", visits, " visits per location")) %>%
  
  group_by(version, design, visits) %>%
  summary_table(var = "est") %>%
  ggplot(aes(x=version, fill=design)) +
  facet_grid(rows = vars(visits), switch = "both") +
  geom_boxplot(position = "dodge", stat="identity", aes(ymin=Q10, lower=Q25, middle=Q50, upper=Q75, ymax=Q90)) +
  geom_hline(yintercept = ref_model_coefs$est, linetype=1, alpha=0.5) +
  geom_hline(yintercept = 0, linetype=2, alpha=0.2) +
  geom_label(data=temp, aes(y=est, label=label), fill= "white",show.legend = F) +
  scale_y_continuous(sec.axis = sec_axis(trans=~(.-tot_pnc)/-tot_pnc, name="Health Point Estimate (% Difference)", labels = scales::percent),
                     position="right") +
  labs(y = "Health Point Estimate",
       fill="Location Visit\nSelection")

 ggsave(file.path(image_path, "presentations", "ufp_health_estimate_sample1.png"), width = 8, height = 5)
  
##################################################################
temp <- data.frame(version=c("All Hr"),
                   label = c("All-Data Reference", "No Association"),
                   est=c(ref_model_coefs$est, 0),
                   design = c(2.7, 2.5), 
                   visits = "~4 visits per location")  
 
#design_levels <- levels(model_coefs$design) %>% gsub(" ", "\n", .)
design_levels <- c("Balanced", "Sensible\nClusters", "Road\nType", "Random\nClusters")
 
print("showing results for non-plume adjusted")
# version 2
model_coefs %>%
  filter(visits==4,
         !design %in% c("Random Segments", "Unsensible Clusters"),
         #adjusted == "Unadjusted"
         #adjusted == "Adjusted"
         ) %>%  
  mutate(visits = paste0("~", visits, " visits per location"),
         version = gsub(" Plume Adj", "", version),
         adjusted = ifelse(adjusted == "Adjusted", "Plume Adjusted Air Measurements", "Unadjusted"),
         design = gsub(" ", "\n", design),
         design = gsub("Balanced", "Balance", design),
         design = factor(design, c("Balance", design_levels))
         ) %>%  
  
  group_by(version, design, visits,
           adjusted, 
           ) %>%
  summary_table(var = "est") %>%
  
  ggplot(aes(fill=adjusted, x=design)) +
  facet_grid(rows = vars(visits),
             cols = vars(version),
             switch = "both") +
  geom_boxplot(position = "dodge", stat="identity", aes(ymin=Q10, lower=Q25, middle=Q50, upper=Q75, ymax=Q90), 
               #col="gray"
               ) +
  geom_hline(yintercept = ref_model_coefs$est, linetype=1, alpha=0.5, col=uw_spirit_purple) +
  geom_hline(yintercept = 0, linetype=2, alpha=0.2) +
  geom_label(data=temp, aes(y=est, label=label), fill= "white",show.legend = F, size=label_size) +
  geom_label(data=filter(temp, grepl("Reference", label, ignore.case = T)), aes(y=est, label=label), fill= "white",col=uw_spirit_purple, show.legend = F, size=label_size) +

  poster_theme +
  theme(panel.background = element_rect(fill = alpha(uw_spirit_gold,0.4))) +
  scale_fill_manual(values = c(uw_spirit_gold, uw_husky_gold
                               #uw_husky_purple, uw_heritage_gold
                               )) +
  
scale_y_continuous(sec.axis = sec_axis(trans=~(.-tot_pnc)/-tot_pnc, name="Health Point Estimate\n % Difference", labels = scales::percent),
                     position="right") + 
  labs(y = "Health Point Estimate",
       x = "Visit Frequency Assignment",
       fill=NULL) 
   

ggsave(file.path(image_path, "presentations", "ufp_health_estimate_sample1_alt.png"), width = 14, height = 8)

```



